Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2021-06-30 ms.tex
proofread

$\square$ Add eigenmodes plots

$\square$ Add discussion of numerical solution of time-dependent equations

$\square$ Add results, summary, conclusions, etc

@@

In the solve step, we evaluate the eigenfunctions at the points $(\chi_{j-1},\chi_{j},\chi_{j+1})$ to obtain the responses $f_{j-1}$, $f_j$, and $f_{j+1}$. A ``guess'' at the correct eigenvalue $\chi_{nm}$ can be calculated from
\be
\chi_{\rm guess} &=& \frac{a\chi_{j-1} - \chi_{j+1}}{a - 1}
\ee
where
\be
a &=& \left(\frac{f_{j} - f_{j-1}}{f_{j} - f_{j+1}}\right)\left(\frac{\chi_{j+1}-\chi_{j}}{\chi_{j-1}-\chi_{j}}\right).
\ee
This is repeated, replacing former points $(\chi_{j-1},\chi_{j},\chi_{j+1})$ with closer estimates while the size of the response grows as we approach the resonance. Given a sufficiently accurate eigenvalue $\chi_{nm}$, we now find the corresponding eigenfunction $J_{nm}(\sigma)$. We can write down an approximate expression for the response near the resonances as
\be
J(n,\sigma,\chi) & \simeq & \frac{J_{nm}(\sigma)}{\chi-\chi_{nm}} + C(\sigma),
\ee
where $C(\sigma)$ is weakly dependent on $\chi$, and so we treat it as a constant. We can now solve for $J_{nm}(\sigma)$ by comparing two points near the resonance:
\be
J(n,\sigma,\chi_1)  - J(n,\sigma,\chi_2)& = &  \frac{J_{nm}(\sigma)}{\chi_1-\chi_{nm}} -  \frac{J_{nm}(\sigma)}{\chi_2-\chi_{nm}}
\ee
where $C(\sigma)$ has cancelled out in the difference. We can immediately solve as
\be
J_{nm}(\sigma) & \simeq & \frac{ J(n,\sigma,\chi_1)  - J(n,\sigma,\chi_2) }{ 1/(\chi_1-\chi_{nm}) - 1/(\chi_2-\chi_{nm})}.
\ee
A set of eigenfunctions $J_{nm}(\sigma)$ are plotted in Fig. \ref{fig:jsoln} to illustrate their relative scales for different frequency eigenmodes $m$ at a fixed spatial eigenmode $n$. Additional terms add smaller, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
\begin{figure}
    \centering
    \includegraphics{Jsoln_n1_m100.pdf}
    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and a range of frequency eigenmodes up to $m=100$. Their oscillatory forms have varying amplitudes which sum to create the final form of the mean intensity. The largest contribution always comes from the ($n=1, m=1$) lowest-order eigenfunction.}
    \label{fig:jsoln}
\end{figure}

>>>>

$\blacksquare$ Add eigenmodes plots

$\blacksquare$ Add discussion of numerical solution of time-dependent equations

$\square$ Add discussion of frequency dependence in time dependent section (spectrum plots?)

$\square$ Add discussion of wait times in time dependent section --- escape time plots, fitting function, etc

$\square$ Add summary to time dependent section

$\square$ Conclusions

@@

In the solve step, we evaluate the eigenfunctions at the points $(\chi_{j-1},\chi_{j},\chi_{j+1})$ to obtain the responses $f_{j-1}$, $f_j$, and $f_{j+1}$. A ``guess'' at the correct eigenvalue $\chi_{nm}$ can be calculated from
\be
\chi_{\rm guess} &=& \frac{a\chi_{j-1} - \chi_{j+1}}{a - 1}
\ee
where
\be
a &=& \left(\frac{f_{j} - f_{j-1}}{f_{j} - f_{j+1}}\right)\left(\frac{\chi_{j+1}-\chi_{j}}{\chi_{j-1}-\chi_{j}}\right).
\ee
This is repeated, replacing former points $(\chi_{j-1},\chi_{j},\chi_{j+1})$ with closer estimates while the size of the response grows as we approach the resonance. Given a sufficiently accurate eigenvalue $\chi_{nm}$, we now find the corresponding eigenfunction $J_{nm}(\sigma)$. We can write down an approximate expression for the response near the resonances as
\be
J(n,\sigma,\chi) & \simeq & \frac{J_{nm}(\sigma)}{\chi-\chi_{nm}} + C(\sigma),
\ee
where $C(\sigma)$ is weakly dependent on $\chi$, and so we treat it as a constant. We can now solve for $J_{nm}(\sigma)$ by comparing two points near the resonance:
\be
J(n,\sigma,\chi_1)  - J(n,\sigma,\chi_2)& = &  \frac{J_{nm}(\sigma)}{\chi_1-\chi_{nm}} -  \frac{J_{nm}(\sigma)}{\chi_2-\chi_{nm}}
\ee
where $C(\sigma)$ has cancelled out in the difference. We can immediately solve as
\be
J_{nm}(\sigma) & \simeq & \frac{ J(n,\sigma,\chi_1)  - J(n,\sigma,\chi_2) }{ 1/(\chi_1-\chi_{nm}) - 1/(\chi_2-\chi_{nm})}.
\ee
\begin{figure}
    \centering
    \includegraphics{Jsoln_n1_m100.pdf}
    \caption{Eigenfunctions $J_{nm}(x)$ for the lowest-order spatial eigenmode $n=1$, and a range of frequency eigenmodes up to $m=100$. Their oscillatory forms have varying amplitudes which sum to create the final form of the mean intensity. The largest contribution always comes from the ($n=1, m=1$) lowest-order eigenfunction.}
    \label{fig:jsoln}
\end{figure}
A set of eigenfunctions $J_{nm}(\sigma)$ are plotted in Fig. \ref{fig:jsoln} to illustrate their relative scales for different frequency eigenmodes $m$ at a fixed spatial eigenmode $n$. Additional terms add smaller, faster-oscillating components that lead to higher accuracy upon summation with the lower-order terms.
